---
title: "Assignment12"
author: "Lilith Holland"
date: '2023-04-02'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data processing and cleaning

## Loading data

For this section I simply wanted to load the data and print the head values.

```{r}
data <- read.csv("./Customers.csv")
head(data)
```

## Data cleaning

After loading the data it became apparent that there is a Null value in the professions column,
and that the column names need to be converted. I am aware there is a built in method
for covering the names however I found it quicker to just print them out than
to look up that method.

```{r}

data['Profession'][data['Profession'] == ""] <- "Misc"
data[c("Gender", "Profession")] <- lapply(data[c("Gender", "Profession")], factor)
names(data) <- c("CustomerID",
                 "Gender",
                 "Age",
                 "Annual_Income",
                 "Spending_Score",
                 "Profession",
                 "Work_Experience",
                 "Family_Size")
head(data)
```

# Plots

## Scatter plot matrix

As a basic exploratory step I decided to create a scatter plot matrix to see how
the different variables interact. It is quickly made apparent that there is no real
pattern to the data that is easily seen.

```{r echo=FALSE}
plot(data[, -which(names(data) %in% c("CustomerID", "Gender",
                                      "Profession", "Family_Size",
                                      "Work_Experience"))])
```
## Scatter plot with fitted line

Following the scatter plot matrix the only real interesting data is the annual income
vs. age as it can provide some potential insight. After reviewing the data it is
quickly made apparent that there is no real relationship between the two variables.

```{r echo=FALSE}
plot(data$Age, data$Annual_Income,
     main="Annual Income vs. Age",
     xlab="Annual Income (USD)",
     ylab="Age (years)")
abline(lm(Annual_Income ~ Age, data=data))
```
## Histogram

The following plot was produced to see if the data was evenly sampled of if there is
a bias towards one group. It is made apparent that people with low work experience
make up a significant portion of the data which could account for why there is
so little variability in annual income.

```{r echo=FALSE}
hist(data$Work_Experience,
     main="Work Experience",
     xlab="Years of Experience")
```